Supplemental material for Tree growth, mortality, and climatic stress in west-coast states, USA

### 2025-12-12 Supplemental Material.Rmd
Incorporated edits from B. Frank.  This added a figure, changed the supplimental and main RMarkdown files, and altered many of the scripts involved in generating plots and tables.

source('Global.R')
source(paste0(CODE.LOC, "Functions.R"))
# Some general analysis info + plots
analysis.stats <- read_rds(paste0(RESULTS.OTHER, "analysis.stats.RDS"))
# Correlation/fits for Initial CWD vs Delta CWD:
CWD.rels <- read_rds(paste0(RESULTS.OTHER, "CWD_deltaCWD_relationship.rds"))

@@

cwd.init <- analysis.stats$init.cwd.stats 
cwd.diff <- analysis.stats$diff.cwd.stats

@@

@@

>>>>

source('Global.R')
source(paste0(CODE.LOC, "Functions.R"))
# Some general analysis info + plots
analysis.stats <- read_rds(paste0(RESULTS.OTHER, "analysis.stats.RDS"))
cwd.init <- analysis.stats$init.cwd.stats  
cwd.diff <- analysis.stats$diff.cwd.stats

# Correlation/fits for Initial CWD vs Delta CWD:
CWD.rels <- read_rds(paste0(RESULTS.OTHER, "CWD_deltaCWD_relationship.rds"))

@@

cwd.init2 <- cwd.init %>% dplyr::select(-UCI, -LCI)
cwd.diff2 <- cwd.diff %>% dplyr::select(-UCI, -LCI)

@@

fig.negcwdmap_cap <- fig_nums(name = "fig_cwdnegmap", 
                        caption = "Fuzzed FIA plot locations for plots with negative CWD values.  The initial CWD values for those plots are displayed in A while the negative delta CWD values are displayed in B.  The inset map (B) shows the locations of the study states within the USA: From north to south, Washington, Oregon, and California.")

@@

```{r cwdfig-negcwdmap, fig.height = 7,  fig.dpi=300, fig.cap=fig.negcwdmap_cap, fig.cap.sep=""}

# Output from Manuscript_information.R
knitr::include_graphics(paste0(RESULTS.OTHER, "cwdneg_maps_figure.png"))
